### 2023-03-30 resilience-safe-down.tex
Currently writing proof

@@

\begin{theorem}\label{up-down}
\textcolor{red}{
The resilience problem is undecidable for WSTS with 
%	more than one minimal element, 
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$.
}
\end{theorem}

\begin{proof}
TBD
\end{proof}

>>>>

\begin{theorem}
The resilience problem is decidable for ideal-effective WSTS with 
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$
and
the additional hypothesis that
for all $D \subseteq S$ downward-closed, $\pred^*(D)$ is downward-closed.
% \alain{est-ce que  $\pred(D)$ is downward closed avec D downward closed serait suffisant ? si l'ordre est omega2 alors closbas+inclusion est wqo donc il faudrait juste que la suite croissante $pred^n(D)+le reste$ converge...}
\end{theorem}

\begin{proof}
By hypothesis $\pred^*(\Safe)$ is downward-closed, since $\Safe$ is downward-closed.
Let $\{J_1, J_2,...,J_n\}$ be the ideal decomposition of $\pred^*(\Safe)$ and $\{b_1,b_2,...,b_m\}$ be the (unique) minimal basis of $\Bad$.
The resilience problem can be reformulated as 
$\uparrow \{b_1,b_2,...,b_m\} \subseteq J_1 \cup J_2 \cup \cdots \cup J_n$.
Since $\mathscr{S}=(S,\rightarrow, \leq)$ is ideally effective, we can compute intersections of closed subsets.
Hence we can compute the intersection of
$\uparrow \{b_1,b_2,...,b_m\}$
and
$S \setminus \pred^*(\Safe)$.
Since
$\uparrow \{b_1,b_2,...,b_m\} \subseteq J_1 \cup J_2 \cup \cdots \cup J_n$
can be reformulated as
$\uparrow \{b_1,b_2,...,b_m\} \cap (S \setminus \pred^*(\Safe)) = \emptyset$
the resilience problem is decidable.
\end{proof}

\begin{corollary}
The resilience problem is decidable for ideal-effective downward-compatible WSTS with 
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$.
\end{corollary}

\begin{proof}

\end{proof}

% \begin{proposition}
In the case

@@
